\LARGE \bf \pyRobots{}, a toolset for robot executive control

### 2014-09-18 paper.tex
Rewritten section on pose management

Managing poses, transformations, frames in real-world scenarios is not an easy
task, mainly because it seems that every single library, middleware or robotic
platform rely on its own conventions (rotation representations, in particular,
are a constant source of frustration, having to jump all the time between
quaternions, one of the 23 Euler conventions, rotation matrices, Rodrigues,
yaw-pitch-roll notation...). Within the ROS ecosystem, the Transform Library
(tf,~\cite{foote2013tf}) has played a major role to make it convenient to work
with frames, and poses can always be expressed and shared in the most convenient
local frame, tf taking care of required intermediate transformation.

\pyRobots{} offers a similar approach \emph{within} the control script, adding a
pinch of syntactic sugar to make poses and frame management transparent for the
high-level action controller.

As illustrated in listing~\ref{lst:poses}, poses can be flexibly defined by a
simple frame name, by a triple $\{x, y, z\}$ (default frame {\tt map} is then
assumed), by a 4-tuple $\{x, y, z, frame\}$, by a 6-tuple $\{x, y, z, rx, ry,
rz\}$ (using $sxyz$ Euler convention), by a 7-tuple $\{x, y, z, rx, ry, rz,
frame\}$, by a 7-tuple $\{x, y, z, qx, qy, qz, qw\}$, by a 8-tuple $\{x, y, z,
qx, qy, qz, qw, frame\}$ or by a dictionary that defines any of these 8 values.
Internally, \pyRobots{} normalizes and stores the poses in their full 8-tuple
expansion.

@@

These transformations are directly computed, but \pyRobots{} also takes advantage
of middleware-specific infrastructure (when available) to provide known frames.
ROS TF, Aldebaran's {\tt NAOqi} frame conventions, etc. are used when available
through specializations of the \pyRobots{} \python|PoseManager| class.

>>>>

Managing poses, transformations, frames in real-world scenarios is not an easy
task, mainly because it seems that every single library, middleware or robotic
platform relies on its own conventions (rotation representations, in particular,
are a common source of inconsistencies -- quaternions, (the many) Euler
conventions, rotation matrices, Rodrigues, yaw-pitch-roll notations being all
rather frequent). Within the ROS ecosystem, the Transform Library ({\sc
tf},~\cite{foote2013tf}) has played a major role to make it convenient to work
with frames, and poses can always be expressed and shared in the most convenient
local frame, {\sc tf} taking care of required intermediate transformation.

\pyRobots{} pose management builds on this idea to offer flexible pose
representations \emph{within} the control scripts. Everytime a 6D pose needs to
be specified (like a navigation goal or a target pose for an arm), it can be
expressed as a simple frame name, by a triple $\{x, y, z\}$ (default frame {\tt
map} is then assumed), by a 4-tuple $\{x, y, z, frame\}$, by a 6-tuple $\{x, y,
z, rx, ry, rz\}$ (using $sxyz$ Euler convention), by a 7-tuple $\{x, y, z, rx,
ry, rz, frame\}$, by a 7-tuple $\{x, y, z, qx, qy, qz, qw\}$, by a 8-tuple $\{x,
y, z, qx, qy, qz, qw, frame\}$ or by a dictionary that defines any subset of
these 8 values.  Internally, \pyRobots{} normalizes and stores the poses in
their full 8-tuple expansion, as illustrated in listing~\ref{lst:poses}.

@@

Required transformations are computed by \pyRobots{}, and the programmer can
provide new ``sources'' of frame transformations through the instanciation of
\python|FrameProviders| that takes advantage of robot- and middleware-specific
infrastructures (for example, ROS {\sc tf}, Aldebaran's {\tt NAOqi} frame
conventions, etc.).
